Multisensor Architecture for an Intersection Management System

### 2018-06-16 ch2-mdf_ims.tex
Added todo notes and some format fixes in chapter 2

@@

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.4]{fig/2/MFIArch.png}
\caption{Multisensor Fusion Integration architecture (from \cite{Luo2011}).}
\label{MFIArch}
\end{figure}

@@

\begin{table}[ht!]
\footnotesize
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{\textbf{Low level fusion}} & \textbf{Medium level fusion} & \textbf{High level fusion} \\
\hline
\multicolumn{2}{|c|}{\textit{Estimation methods}} & \textit{Classification methods} & \textit{Inference methods} \\
\hline
\parbox{2.5cm}{
	Recursive:
	\begin{itemize}[leftmargin=.07in]
		\item Kalman filter
		\item Extended Kalman filter
	\end{itemize}
	Non-Recursive:
	\begin{itemize}[leftmargin=.07in]
		\item Weighted average
		\item Least squares
	\end{itemize}
	}
 & 
 \parbox{2.5cm}{	 
 	Covariance-based:
	\begin{itemize}[leftmargin=.07in]
		\item Cross covariance
		\item Covariance intersection
		\item Covariance union
	\end{itemize}
	}
&
 \parbox{3cm}{	 
	\begin{itemize}[leftmargin=.07in, noitemsep]
		\item Parametric templates
		\item Cluster analysis
		\item K-means clustering
		\item Learning vector quantization
		\item Kohonen feature map
		\item Artificial neural networks
		\item Support vector machines
	\end{itemize}
	}
&
\parbox{3cm}{	 
	\begin{itemize}[leftmargin=.07in, noitemsep]
		\item Bayesian inference
		\item Particle filters
		\item Dempster-Shafer theory
		\item Expert systems
		\item Fuzzy logic
	\end{itemize}
	} \\
\hline
\end{tabular}
\caption{Classification of fusion algorithms based on level of fusion}
\label{fusionAlgClasLuo}
\end{table}

@@

\begin{table}[!t]
\begin{tabular}{|p{0.13\linewidth}|c|p{0.125\linewidth}|p{0.15\linewidth}|p{0.16\linewidth}|c|}
\hline

\textbf{Reference} & \textbf{Project} & \textbf{Sensors} & \textbf{Target} & \textbf{Fusion} & \textbf{Framework} \\
\hline

\cite{Zhao2006} & POSSi & Laser & Vehicles, pedestrians & - & No \\
\hline

\cite{Song2008} & POSSi & Lasers & Pedestrians & Low-Level & No \\
\hline

\cite{Zhao2008} & POSSi & Lasers & Vehicles, pedestrians & Low-Level & No \\
\hline

\cite{Zhao2009} & POSSi & Lasers, Camera & Vehicles, pedestrians & Low-Level, High-Level & No \\
\hline

\cite{Zhao2012} & POSSi & Lasers & Vehicles, pedestrians & Low-Level & No \\
\hline

\cite{Goldhammer2012} & Ko-PER & Lasers, Cameras & Vehicles, pedestrians & Low-Level, Mid-Level & No \\
\hline

\cite{Meissner2012} & Ko-PER & Lasers & Pedestrians & Low-Level & No \\
\hline

\cite{Meissner2013} & Ko-PER & Lasers & Vehicles, pedestrians & Low-Level & No \\
\hline

\cite{Meissner2013a, Meissner2013b} & Ko-PER & Lasers, Cameras & Vehicles, pedestrians & Low-Level, Mid-Level & No \\
\hline

\cite{Strigel2013} & Ko-PER & Cameras & Vehicles & Low-Level & No \\
\hline

\cite{Meissner2014} & Ko-PER & Lasers, Cameras & Vehicles, pedestrians & Low-Level, Mid-Level & No \\
\hline

@@

\textbf{Proposed work} & - & \textbf{Lasers, Cameras} & \textbf{Vehicles} & \textbf{Low-Level, Mid-Level, High-Level} & \textbf{Yes} \\
\hline

>>>>

\todo{Create custom figure}

@@

\todo{Increase font size of this figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.5]{fig/2/MFIArch.png}
\caption{Multisensor Fusion Integration architecture (from \cite{Luo2011}).}
\label{MFIArch}
\end{figure}

@@

\begin{table}[ht!]
\footnotesize
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{\textbf{Low level fusion}} & \textbf{Medium level fusion} & \textbf{High level fusion} \\
\hline
\multicolumn{2}{|c|}{\textit{Estimation methods}} & \textit{Classification methods} & \textit{Inference methods} \\
\hline
\parbox{2.4cm}{
	Recursive:
	\begin{itemize}[leftmargin=.07in]
		\item Kalman filter
		\item Extended Kalman filter
	\end{itemize}
	Non-Recursive:
	\begin{itemize}[leftmargin=.07in]
		\item Weighted average
		\item Least squares
	\end{itemize}
	}
 & 
 \parbox{2.4cm}{	 
 	Covariance-based:
	\begin{itemize}[leftmargin=.07in]
		\item Cross covariance
		\item Covariance intersection
		\item Covariance union
	\end{itemize}
	}
&
 \parbox{3cm}{	 
	\begin{itemize}[leftmargin=.07in, noitemsep]
		\item Parametric templates
		\item Cluster analysis
		\item K-means clustering
		\item Learning vector quantization
		\item Kohonen feature map
		\item Artificial neural networks
		\item Support vector machines
	\end{itemize}
	}
&
\parbox{2.9cm}{	 
	\begin{itemize}[leftmargin=.07in, noitemsep]
		\item Bayesian inference
		\item Particle filters
		\item Dempster-Shafer theory
		\item Expert systems
		\item Fuzzy logic
	\end{itemize}
	} \\
\hline
\end{tabular}
\caption{Classification of fusion algorithms based on level of fusion}
\label{fusionAlgClasLuo}
\end{table}

@@

\begin{table}[!t]
\begin{tabular}{|c|p{0.125\linewidth}|p{0.15\linewidth}|p{0.16\linewidth}|c|}
\hline

\textbf{Project} & \textbf{Sensors} & \textbf{Target} & \textbf{Fusion} & \textbf{Framework} \\
\hline

POSSi \cite{Zhao2006}& Laser & Vehicles, pedestrians & - & No \\
\hline

POSSi \cite{Song2008}& Lasers & Pedestrians & Low-Level & No \\
\hline

POSSi \cite{Zhao2008}& Lasers & Vehicles, pedestrians & Low-Level & No \\
\hline

POSSi \cite{Zhao2009}& Lasers, Camera & Vehicles, pedestrians & Low-Level, High-Level & No \\
\hline

POSSi \cite{Zhao2012}& Lasers & Vehicles, pedestrians & Low-Level & No \\
\hline

Ko-PER \cite{Goldhammer2012} & Lasers, Cameras & Vehicles, pedestrians & Low-Level, Mid-Level & No \\
\hline

Ko-PER \cite{Meissner2012} & Lasers & Pedestrians & Low-Level & No \\
\hline

Ko-PER \cite{Meissner2013} & Lasers & Vehicles, pedestrians & Low-Level & No \\
\hline

Ko-PER \cite{Meissner2013a, Meissner2013b} & Lasers, Cameras & Vehicles, pedestrians & Low-Level, Mid-Level & No \\
\hline

Ko-PER \cite{Strigel2013}& Cameras & Vehicles & Low-Level & No \\
\hline

Ko-PER \cite{Meissner2014}& Lasers, Cameras & Vehicles, pedestrians & Low-Level, Mid-Level & No \\
\hline

@@

\textbf{Proposed work} & \textbf{Lasers, Cameras} & \textbf{Vehicles} & \textbf{Low-Level, Mid-Level, High-Level} & \textbf{Yes} \\
\hline
